Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-17 index.Rmd
update button

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
load("bb_issuersTOOL.Rdata")

if(run_shiny_tool) suppressPackageStartupMessages({
  library(htmlwidgets)
  library(shiny)
  library(shinyjs)
  library(shinysky) #  devtools::install_github("AnalytixWare/ShinySky")
  library(dygraphs)
  library(Rcpp)
  library(RcppArmadillo)
  library(stringr)
  library(gtools)
  library(timeDate)
})

@@

source("lib_helpers.R", local = TRUE)
source("latex_code.R")
source("ff_industries_sic.R")
source("Paper_global_parameters.R")
source("heatmapOutput.R") 
source("ff_industries_sic.R")

@@

**NOTE:** Please always wait until all tables load (and "fade in")...

This is an interactive tool for the article [Volatility and the Buyback Anomaly](http://tevgeniou.github.io/BuybacksIssuers/). Users can explore the effects of various parameters as well as data filtering choices. For any given choices, users can generate and download a new **customized pdf version of the paper** (work in progress) by clicking the button below at any time.

**Note that it takes a few minutes (possibly more than five) to compile the new paper. Please wait until the option to download the paper, becomes available.**

```{r, fig.width=6, fig.height=5,echo=FALSE}
useShinyjs(rmd=TRUE)
fluidPage(
  shiny::actionButton("compileReport","Compile Paper",icon=icon("spinner")),
  shiny::downloadButton("downloadReport", "Download Paper")
)
report.data <- paste0("session.", session$token, ".report.data.Rdata")
report.script <- paste0("session.", session$token, ".report.script.R")
report.source <- paste0("session.", session$token, ".report.Rnw")
report.file <- paste0("session.", session$token, ".report.pdf")
observeEvent(input$compileReport, {
  disable("compileReport")
  with(report.list <- new.env(), {
    startdate <- isolate(input$startdate)
    enddate <- isolate(input$enddate)
    market_cap_min <- isolate(input$market_cap_min)
    market_cap_max <- isolate(input$market_cap_max)
    characteristic <- isolate(input$characteristic)
    characteristic_single_analysis <- isolate(input$characteristic_single_analysis)
    quantile_used <- isolate(input$quantile_used)
    characteristic_single_analysis_sign <- isolate(input$characteristic_single_analysis_sign)
    high_EU_index_thres <- isolate(input$high_EU_index_thres)
    low_EU_index_thres <- isolate(input$low_EU_index_thres)
    quantile_used_ind <- isolate(input$quantile_used_ind)
    quantile_used_all <- isolate(input$quantile_used_all)
    characteristic_irats1 <- isolate(input$characteristic_irats1)
    characteristic_irats2 <- isolate(input$characteristic_irats2)
    characteristic_irats3 <- isolate(input$characteristic_irats3)
    characteristic_irats4 <- isolate(input$characteristic_irats4)
    characteristic_irats5 <- isolate(input$characteristic_irats5)
    characteristic_irats6 <- isolate(input$characteristic_irats6)
    characteristic_irats1_sign <- isolate(input$characteristic_irats1_sign)
    characteristic_irats2_sign <- isolate(input$characteristic_irats2_sign)
    characteristic_irats3_sign <- isolate(input$characteristic_irats3_sign)
    characteristic_irats4_sign <- isolate(input$characteristic_irats4_sign)
    characteristic_irats5_sign <- isolate(input$characteristic_irats5_sign)
    characteristic_irats6_sign <- isolate(input$characteristic_irats6_sign)
    industry <- isolate(input$industry)
  })
  for (x in ls(report.list)) if (is.null(get(x, report.list))) warning(paste0("parameter '", x, "' is NULL"), call.=FALSE, immediate.=TRUE)
  save(report.list, file=report.data)
  file.copy("toolreport.Rnw", report.source)
  cat(paste0("load ('", report.data, "')\n"), file=report.script)
  cat(paste0("knitr::knit2pdf('", report.source,"', quiet=TRUE)\n"), file=report.script, append=TRUE)
  system(paste0("Rscript --vanilla ", report.script), wait=FALSE)
})
observe({
  invalidateLater(1000, session)
  toggleState("downloadReport", condition=file.exists(report.file))
})
output$downloadReport <- downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    file.copy(report.file, file)
    file.remove(list.files(pattern=paste0("session.", session$token)))
    enable("compileReport")
    disable("downloadReport")
  }
)
```

@@

You can select some filters for the dataset. All analyses below will be done only for the events that are selected.

Every time you change these filters you may **need to wait a few seconds** until all results of this tool are updated (all tables/figures "fade in").

Select the time period for which you would like to do the analyses below:

```{r, eval=TRUE, echo = FALSE}
dateInput("startdate", "Starting Date:", 
          value = min(BUYBACK_DATA_TOOL$Event.Date) - 10, min = min(BUYBACK_DATA_TOOL$Event.Date), max = max(BUYBACK_DATA_TOOL$Event.Date)-3*370,
          startview = "year",
          width='100%')
```
<br>
```{r, eval=TRUE, echo = FALSE}
dateInput("enddate", "End Date (allow at least 3 years from the starting day you selected - else it will automatically use data up to 3 years after your start date):", 
          value = max(BUYBACK_DATA_TOOL$Event.Date) + 10, 
          min = min(BUYBACK_DATA_TOOL$Event.Date)+3*370, 
          max = max(BUYBACK_DATA_TOOL$Event.Date)+10,startview = "year",
          width='100%')
```

Selet the minimum size of the firms (in $millions) for which you would like to do the analyses below. The maximum selected should be larger than the minimum, else the maximum is automatically set to infinity:

```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")
```
<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), 10e10)), selected = as.character(10e10), width = "1000px")
```

We can also see the effects of removing some industries: we can select industries to remove here (make sure there are enough data left for the analysis):

```{r, eval=TRUE, echo = FALSE}
selectInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,multiple=TRUE,width="100%") 
```
<br>

```{r, eval=TRUE, echo = FALSE}
DATASET_NEW <- reactive({
  starting = input$startdate 
  ending = input$enddate   
  if (ending - starting < 3*365)
    ending = starting + 3*365

@@

  list(
    BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
    returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
    DatesMonth  = DatesMonth[,useonly_report],
    value.weights = value.weights[useonly_report],
    subset = useonly_report
  )
})

@@

@@

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
  quantile_used_ind = as.numeric(input$quantile_used)

@@

feature_CALtable <- reactive({
  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
  quantile_used_ind = as.numeric(input$quantile_used)

@@

  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

High_feature_Hedged_react <- reactive({
  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
  quantile_used_ind = as.numeric(input$quantile_used)

@@

  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
})

Low_feature_Hedged_react <- reactive({
  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
  quantile_used_ind = as.numeric(input$quantile_used)

@@

  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

@@

@@

```{r, eval=TRUE, echo = FALSE}
EU_index_table <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]
  res = matrix(table(thefeature),nrow=1)
  colnames(res) <- paste("EU Index", names(table(thefeature)), sep=": ")
  rownames(res) <- "# of Events"
  res
})

feature_IRATStable_industry <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]

@@

  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low EU: CAR", "t-stat","p-value", "High EU: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]

@@

  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events],
                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
  ),2)[reported_times,]
  colnames(res) <- c("Low EU: CAL", "t-stat","p-value", "High EU: CAL", "t-stat","p-value")
  as.data.frame(res)
})

@@

```{r, eval=TRUE, echo = FALSE}
selected_features = reactive({
  paste(setdiff(unique(c(input$characteristic_irats1,input$characteristic_irats2,input$characteristic_irats3,input$characteristic_irats4,input$characteristic_irats5,input$characteristic_irats6)), "None"), sep=",")
})

@@

Index_Score_rect <- reactive({

@@

feature_IRATStable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))

  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[, High_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

feature_CALtable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))

@@

  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  res
})

High_feature_Hedged_react_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
})

Low_feature_Hedged_react_index <- reactive({
  thefeature = Index_Score_rect()
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

>>>>

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
load("bb_issuersTOOL.Rdata")
BUYBACK_DATA_TOOL$Industry_name <- as.character(BUYBACK_DATA_TOOL$Industry_name)

if(run_shiny_tool) suppressPackageStartupMessages({
  library(htmlwidgets)
  library(shiny)
  suppressWarnings(library(shinyjs))
  library(shinysky) #  devtools::install_github("AnalytixWare/ShinySky")
  library(dygraphs)
  library(Rcpp)
  library(RcppArmadillo)
  library(stringr)
  library(gtools)
  library(timeDate)
})

@@

source("lib_helpers.R", local = TRUE)
source("latex_code.R")
source("ff_industries_sic.R")
source("Paper_global_parameters.R")
source("heatmapOutput.R") 
source("ff_industries_sic.R")
useShinyjs(rmd=TRUE)

@@

This is an interactive tool for the article [Volatility and the Buyback Anomaly](http://tevgeniou.github.io/BuybacksIssuers/). Users can explore the effects of various parameters as well as data filtering choices. Every time you change the parameters below, you can click on the **"Update Results"** button to see the new results. You may **need to wait a few seconds** until all results of this tool are updated (all tables/figures "fade in").

```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```
<br>

For any given choices of parameters, you can also download a pdf version of the results for the data sample you selected by clicking on the **Compile Report** button. **Note that it takes a few minutes (possibly more than five) to compile the new paper. Please wait until the option to download the paper, becomes available.**

```{r, fig.width=6, fig.height=5,echo=FALSE}
useShinyjs(rmd=TRUE)
fluidPage(
  shiny::actionButton("compileReport","Compile Report",icon=icon("spinner")),
  shiny::downloadButton("downloadReport", "Download Report")
)
```

@@

You can select some filters for the dataset. All analyses below will be done only for the events that are selected. 
<br>
Select the time period, the minimum and maximum market capitalization of the firms (in $millions - the maximum selected should be larger than the minimum, else the maximum is automatically set to infinity) for which you would like to do the analyses below. You can also see the effects of removing some industries by selecting also any industries to remove (make sure there are enough data left for the analysis)

```{r, fig.width=6, fig.height=5,echo=FALSE}

report.data <- paste0("session.", session$token, ".report.data.Rdata")
report.script <- paste0("session.", session$token, ".report.script.R")
report.source <- paste0("session.", session$token, ".report.Rnw")
report.file <- paste0("session.", session$token, ".report.pdf")
observeEvent(input$compileReport, {
  disable("compileReport")
  with(report.list <- new.env(), {
    startdate <- isolate(input$startdate)
    enddate <- isolate(input$enddate)
    market_cap_min <- isolate(input$market_cap_min)
    market_cap_max <- isolate(input$market_cap_max)
    characteristic <- isolate(input$characteristic)
    characteristic_single_analysis <- isolate(input$characteristic_single_analysis)
    quantile_used <- isolate(input$quantile_used)
    characteristic_single_analysis_sign <- isolate(input$characteristic_single_analysis_sign)
    high_EU_index_thres <- isolate(input$high_EU_index_thres)
    low_EU_index_thres <- isolate(input$low_EU_index_thres)
    quantile_used_ind <- isolate(input$quantile_used_ind)
    quantile_used_all <- isolate(input$quantile_used_all)
    characteristic_irats1 <- isolate(input$characteristic_irats1)
    characteristic_irats2 <- isolate(input$characteristic_irats2)
    characteristic_irats3 <- isolate(input$characteristic_irats3)
    characteristic_irats4 <- isolate(input$characteristic_irats4)
    characteristic_irats5 <- isolate(input$characteristic_irats5)
    characteristic_irats6 <- isolate(input$characteristic_irats6)
    characteristic_irats1_sign <- isolate(input$characteristic_irats1_sign)
    characteristic_irats2_sign <- isolate(input$characteristic_irats2_sign)
    characteristic_irats3_sign <- isolate(input$characteristic_irats3_sign)
    characteristic_irats4_sign <- isolate(input$characteristic_irats4_sign)
    characteristic_irats5_sign <- isolate(input$characteristic_irats5_sign)
    characteristic_irats6_sign <- isolate(input$characteristic_irats6_sign)
    industry <- isolate(input$industry)
  })
  for (x in ls(report.list)) if (is.null(get(x, report.list))) warning(paste0("parameter '", x, "' is NULL"), call.=FALSE, immediate.=TRUE)
  save(report.list, file=report.data)
  file.copy("toolreport.Rnw", report.source)
  cat(paste0("load ('", report.data, "')\n"), file=report.script)
  cat(paste0("knitr::knit2pdf('", report.source,"', quiet=TRUE)\n"), file=report.script, append=TRUE)
  system(paste0("Rscript --vanilla ", report.script), wait=FALSE)
})
observe({
  invalidateLater(1000, session)
  toggleState("downloadReport", condition=file.exists(report.file))
})

dateInput("startdate", "Starting Date:", 
          value = min(BUYBACK_DATA_TOOL$Event.Date) - 10, min = min(BUYBACK_DATA_TOOL$Event.Date), max = max(BUYBACK_DATA_TOOL$Event.Date)-3*370,
          startview = "year",
          width='100%')
dateInput("enddate", "End Date (allow at least 3 years from the starting day you selected - else it will automatically use data up to 3 years after your start date):", 
          value = max(BUYBACK_DATA_TOOL$Event.Date) + 10, 
          min = min(BUYBACK_DATA_TOOL$Event.Date)+3*370, 
          max = max(BUYBACK_DATA_TOOL$Event.Date)+10,startview = "year",
          width='100%')

selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")

selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), 10e10)), selected = as.character(10e10), width = "1000px")

selectInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,multiple=TRUE,width="100%")

output$downloadReport <- downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    file.copy(report.file, file)
    file.remove(list.files(pattern=paste0("session.", session$token)))
    enable("compileReport")
    disable("downloadReport")
  }
)
```

```{r, eval=TRUE, echo = FALSE}
DATASET_NEW <- reactive({
  input$computeButton
  isolate({

    starting = input$startdate 
    ending = input$enddate   
    if (ending - starting < 3*365)
      ending = starting + 3*365

@@

    list(
      BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
      returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
      DatesMonth  = DatesMonth[,useonly_report],
      value.weights = value.weights[useonly_report],
      subset = useonly_report
    )
  })
})

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```

@@

feature_IRATStable <- reactive({
  input$computeButton
  isolate({

    thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
    thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
    thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
    quantile_used_ind = as.numeric(input$quantile_used)

@@

feature_CALtable <- reactive({
  input$computeButton
  isolate({

    thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
    thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
    thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
    quantile_used_ind = as.numeric(input$quantile_used)

@@

    colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
    as.data.frame(res)
  })
})

High_feature_Hedged_react <- reactive({
  input$computeButton
  isolate({

    thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
    thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
    thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
    quantile_used_ind = as.numeric(input$quantile_used)

@@

    High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
    remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
  })
})

Low_feature_Hedged_react <- reactive({
  input$computeButton
  isolate({

    thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
    thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
    thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
    quantile_used_ind = as.numeric(input$quantile_used)

@@

    Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
    remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade) 
  })
})

@@

<br> 
```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```
<br>

@@

<br>
```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```
<br>

```{r, eval=TRUE, echo = FALSE}
EU_index_table <- reactive({
  input$computeButton
  isolate({

    thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]
    res = matrix(table(thefeature),nrow=1)
    colnames(res) <- paste("EU Index", names(table(thefeature)), sep=": ")
    rownames(res) <- "# of Events"
    res
  })
})

feature_IRATStable_industry <- reactive({
  input$computeButton
  isolate({

    thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]

@@

    res = round(cbind(
      car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events],
                DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
      car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
                DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
    ),2)[reported_times,]
    colnames(res) <- c("Low EU: CAR", "t-stat","p-value", "High EU: CAR", "t-stat","p-value")
    as.data.frame(res)
  })
})

feature_CALtable_industry <- reactive({
  input$computeButton
  isolate({

    thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]

@@

    res = round(cbind(
      calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events],
                     DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
      calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
                     DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
    ),2)[reported_times,]
    colnames(res) <- c("Low EU: CAL", "t-stat","p-value", "High EU: CAL", "t-stat","p-value")
    as.data.frame(res)
  })
})

@@

<br>
```{r, fig.width=6, fig.height=5,echo=FALSE}
fluidPage(shiny::actionButton("computeButton","Update Results",icon=icon("spinner")) )
```
<br>

```{r, eval=TRUE, echo = FALSE}
selected_features = reactive({
  input$computeButton
  isolate({

    paste(setdiff(unique(c(input$characteristic_irats1,input$characteristic_irats2,input$characteristic_irats3,input$characteristic_irats4,input$characteristic_irats5,input$characteristic_irats6)), "None"), sep=",")
  })
})
```

@@

Index_Score_rect <- reactive({
  input$computeButton
  isolate({

@@

  })
})

feature_IRATStable_index <- reactive({
  input$computeButton
  isolate({

    thefeature = Index_Score_rect()
    High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
    Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))

    res = round(cbind(
      car_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
                DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
      car_table(DATASET_NEW()$returns_by_event_monthly[, High_feature_events],
                DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
    ),2)[reported_times,]
    colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
    res
  })
})

feature_CALtable_index <- reactive({
  input$computeButton
  isolate({

    thefeature = Index_Score_rect()
    High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
    Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))

@@

    colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
    res
  })
})

High_feature_Hedged_react_index <- reactive({
  input$computeButton
  isolate({

    thefeature = Index_Score_rect()
    High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
    High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
    remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
  })
})
Low_feature_Hedged_react_index <- reactive({
  input$computeButton
  isolate({

    thefeature = Index_Score_rect()
    Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
    Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
    remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
  })
})
